### 2013-03-25 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
updating emission kernel integrand in transport equation and citation syntax in spn equations

The neutron transport problem is complicated. Solutions cover a large
phase space and the problems of interest are often geometrically
complex, very large, or both, requiring tremendous computational
resources to generate an adequate solution. Modern deterministic
methods for large scale problems are commonly variants on the discrete
ordinates ($S_N$) method \cite{evans_denovo:_2010}. For full reactor
core neutronics simulations, the $S_N$ method requires potentially
trillions of unknown angular flux moments to be computed to achieve
good accuracy for the repsonses of interest. Other forms of the
transport problem, including the $P_N$ method, take on a simpler form
than the more common $S_N$ methods but lack in accuracy when compared
while still requiring considerable computational resources for
solutions in multiple dimensions.

@@

In this document we derive the multigroup $SP_N$ equations from the
Boltzmann transport equation. We then perform a spectral analysis on
the resulting system of equations to determine its potential
performance with both modern Krylov methods and Monte Carlo methods
for asymmetric linear systems. Following this, we devise a Monte Carlo
synthetic acceleration method as a proposed solution scheme.

@@

%%---------------------------------------------------------------------------%%
\section{The Neutron Transport Equation}
\label{sec:transport_eq}
As a starting point we define the time-independent neutron transport
equation \cite{lewis_computational_1993}:
\begin{multline}
  \hat{\Omega} \cdot \vec{\nabla} \psi(\vec{r},\hat{\Omega},E) +
  \sigma(\vec{r},E) \psi(\vec{r},\hat{\Omega},E) = \\ \int \int
  \sigma_s(\vec{r},E' \rightarrow E,\hat{\Omega}' \rightarrow
  \hat{\Omega}) \psi(\vec{r},\hat{\Omega}',E') d\Omega' dE' +
  q(\vec{r},\hat{\Omega},E)\:,
  \label{eq:general_transport}
\end{multline}
with the variables defined as:
\begin{itemize}
\item $\vec{r}$ - neutron spatial position
\item $\hat{\Omega}$ - neutron streaming direction with radial
  component $\mu$ and azimuthal component $\omega$
\item $\hat{\Omega}' \cdot \hat{\Omega} = \mu_0$ is the angle of
  scattering
\item $E$ - neutron energy
\item $\psi(\vec{r},\hat{\Omega},E)$ - angular flux
\item $\sigma(\vec{r},E)$ - total interaction cross section
\item $\sigma_s(\vec{r},E' \rightarrow E,\hat{\Omega}')$ - probability
  of scattering from direction $\hat{\Omega}'$ into an angular domain
  $d\hat{\Omega}'$ about the direction $\hat{\Omega}$ and from energy
  $E'$ to an energy domain $dE'$ about energy $E$
\item $q(\vec{r},\hat{\Omega},E)$ - external source of neutrons.
\end{itemize}
For this work, it is sufficient to formulate
Eq~(\ref{eq:general_transport}) in 1-dimensonal Cartesian geometry:
\begin{multline}
  \mu \frac{\partial}{\partial x} \psi(x,\mu,E) + \sigma(x,E)
  \psi(x,\mu,E) = \\ \int \int \sigma_s(x,E') \rightarrow
  E,\hat{\Omega}' \rightarrow \hat{\Omega}) \psi(x,\hat{\Omega}',E')
  d\Omega' dE' + \frac{q(x,E)}{4 \pi}\:,
  \label{eq:cart_1d_transport}
\end{multline}
where the angular component of the solution is no longer dependent on
the azimuthal direction of travel and an isotropic source of neutrons
is assumed.

@@

\subsection{Legendre Polynomials}
\label{subsec:legendre_polys}
The Legendre polynomials are an orthogonal set of functions that
are solutions to Legendre's differential equation. They have the
following form \cite{lewis_computational_1993}:
\begin{equation}
  P_l(\mu) = \frac{1}{2^l l!}\frac{d^l}{d \mu^l}(\mu^2-1)^l\:.
  \label{eq:general_legendre_poly}
\end{equation}
These functions have several useful properties including
orthogonality:
\begin{equation}
  \int_{-1}^{1} P_l(\mu) P_{l'}(\mu) d\mu = \frac{1}{2l+1}\delta_{l l'}\:,
  \label{eq:legendre_orthog}
\end{equation}
a recurrence relation:
\begin{equation}
  \mu P_l(\mu) = \frac{1}{2l+1}[(l+1)P_{l+1}(\mu) + l P_{l-1}(\mu)]\:,
  \label{eq:legendre_recurrence}
\end{equation}
and an addition theorem:
\begin{equation}
  P_l(\hat{\Omega} \cdot \hat{\Omega}') = \frac{1}{2n+1}\sum_{m=-l}^l
  Y_{lm}(\hat{\Omega})Y^*_{lm}(\hat{\Omega}')\:,
  \label{eq:legendre_addition}
\end{equation}
where the functions $Y_{lm}(\hat{\Omega})$ are the spherical
harmonics. We can form the addition theorem in this way because the
spherical harmonics are in fact just harmonic multiples of the
Legendre polynomials:
\begin{equation}
  Y_{lm}(\hat{\Omega}) =
  \sqrt{\frac{(2l+1)(l-m)!}{(l+m)!}}P^m_l(\mu)e^{i \omega m}\:,
  \label{eq:spherical_harmonic}
\end{equation}
where $\omega$ is the azimuthal component of the streaming
direction. We can reduce Eq~(\ref{eq:legendre_addition}) for the
planar geometry we are studying by ignoring the azimuthal components
of the addition theorem. As shown in Eq~(\ref{eq:spherical_harmonic}),
the azimuthal dependence is given by the harmonic component, $e^{i
  \omega m}$, and therefore we choose to ignore all terms in
Eq.~(\ref{eq:legendre_addition}) where $m \neq 0$. This gives:
\begin{equation}
  P_l(\hat{\Omega} \cdot \hat{\Omega}') = \frac{1}{2n+1}
  Y_{l0}(\hat{\Omega})Y^*_{l0}(\hat{\Omega}')\:.
  \label{eq:legendre_addition_2}
\end{equation}
Per Eq~(\ref{eq:spherical_harmonic}) we have:
\begin{equation}
  Y_{l0}(\hat{\Omega}) = \sqrt{2l+1}P_l^0(\mu)\:,
  \label{eq:harmonic_0}
\end{equation}
where $P_l^0(\mu) = P_l(\mu)$ is the $0^{th}$ associated Legendre
function. Finally, we can reduce the addition theorem from
Eq~(\ref{eq:legendre_addition_2}) with Eq~(\ref{eq:harmonic_0}) to a
simple product for planar geometry:
\begin{equation}
  P_l(\hat{\Omega} \cdot \hat{\Omega}') = P_l(\mu)P_l(\mu')\:.
  \label{eq:legendre_addition_3}
\end{equation}

\subsection{Planar $P_N$ Equations}
\label{subsec:planar_pn}
With the Legendre polynomial properties defined above, we can proceed
by deriving the $P_N$ equations for planar geometry. For these
equations, we will start by assuming a monoenergtic field of neutrons
such that we are solving the following reduced form of the transport
equation: 
\begin{equation}
  \mu \frac{\partial}{\partial x} \psi(x,\mu) + \sigma(x) \psi(x,\mu)
  = \int d\Omega' \sigma_s(x,\hat{\Omega}' \rightarrow \hat{\Omega})
  \psi(\vec{r},\hat{\Omega}') + \frac{q(x)}{4 \pi}\:.
  \label{eq:mono_transport}
\end{equation}
The $P_N$ equations introduce the approximation that the angular
dependence of the scattering cross section, $\sigma_s$, and the angular
flux $\psi$, can be discretized by expanding them in Legendre
polynomials as follows:
\begin{equation}
  \psi(x,\mu) = \sum_{n=0}^\infty (2n+1)P_n(\mu)\phi_n(x)\:,
  \label{eq:flux_expansion}
\end{equation}
\begin{equation}
  \sigma_{sm}(x) = \sum_{m=0}^\infty (2m+1)P_m(\mu)\sigma_s(x)\:,
  \label{eq:scattering_expansion}
\end{equation}
where we have supressed the $2\pi$ generated by integrating away the
azimuthal angular component and $\phi_n(x)$ in
Eq~(\ref{eq:flux_expansion}) is referred to as the $n^{th}$ Legendre
moment of the neutron flux and is given by:
\begin{equation}
  \phi_n(x) = \int_{-1}^1 P_n(\mu)\psi(x,\mu)d\mu\:.
  \label{eq:legendre_moments}
\end{equation}
We first insert the expansions given by Eq~(\ref{eq:flux_expansion})
and (\ref{eq:scattering_expansion}) into the planar transport equation
given by Eq~(\ref{eq:mono_transport}):
\begin{multline}
  \frac{\partial}{\partial x}\Big[\sum_{n=0}^\infty (2n+1) \phi_n \mu
    P_n(\mu) \Big] + \sigma \sum_{n=0}^\infty (2n+1) \phi_n P_n(\mu) =
  \\ \int_{-1}^1 \sum_{m=0}^\infty (2m+1) \sigma_{sm} P_m(\mu_0)
  \sum_{n=0}^\infty (2n+1) \phi_n P_n(\mu') d \mu' + q\:,
  \label{eq:pn_deriv_1}
\end{multline}
where the dependence on the spatial variable, $x$, has been
supressed. To arrive at the $P_N$ equations we multiply
Eq~(\ref{eq:pn_deriv_1}) by $P_m(\mu)$ and integrate over the angular
domain $\int_{-1}^1 d \mu$. We will look at each term in
Eq~(\ref{eq:pn_deriv_1}) individually.

@@

Now that we have expanded all angular dependent terms in
Eq~(\ref{eq:pn_deriv_1}) and reduced them appropriately, we can
combine them to generate the $P_N$ equations:
\begin{equation}
    \sum_{n=0}^\infty \frac{\partial}{\partial x} \frac{1}{2n+1} \Big[
      (n+1) \phi_{n+1} + n \phi_{n-1} \Big] + \sum_{n=0}^\infty \sigma
    \phi_n = \sum_{n=0}^\infty \sigma_{sn} \phi_n + q\delta_{n0}\:.
  \label{eq:pn_deriv_18}
\end{equation}
More formally, the $P_N$ equations are written as:
\begin{equation}
   \frac{1}{2n+1} \frac{\partial}{\partial x}\Big[ (n+1) \phi_{n+1} + n
     \phi_{n-1} \Big] + \Sigma_n \phi_n = q\delta_{n0} \:,
  \label{eq:final_pn_equations}
\end{equation}
where $\Sigma_n = \sigma-\sigma_{sn}$ and the summations are truncated
at some level of approximation $N$ such that $n = 0,1,\dotsc,N$. This
yields a set of $N+1$ equations for $N+2$ flux moments. We therefore
require an additional equation to close the system. In accordance with
the series truncation as an approximation we choose the last moment in
the expansion to be zero:
\begin{equation}
  \phi_{N+1} = 0\:.
  \label{eq:pn_closure}
\end{equation}
As an example, we will construct the P5 equations from
Eq~(\ref{eq:final_pn_equations}) and the closure given by
Eq~(\ref{eq:pn_closure}):
\begin{subequations}
  \begin{gather}
   \frac{\partial}{\partial x}\phi_{1} + \Sigma_0 \phi_0 = q\:,\\ 
   \frac{1}{3} \frac{\partial}{\partial x}\Big[ 2
     \phi_{2} + \phi_{0} \Big] + \Sigma_1 \phi_1 = 0\:,\\
   \frac{1}{5} \frac{\partial}{\partial x}\Big[ 3 \phi_{3} + 2
     \phi_{1} \Big] + \Sigma_2 \phi_2 = 0 \:,\\
   \frac{1}{7} \frac{\partial}{\partial x}\Big[ 4 \phi_{4} + 3
     \phi_{2} \Big] + \Sigma_3 \phi_3 = 0 \:,\\
   \frac{1}{9} \frac{\partial}{\partial x}\Big[ 5 \phi_{5} + 4
     \phi_{3} \Big] + \Sigma_4 \phi_4 = 0 \:,\\
   \frac{1}{11} \frac{\partial}{\partial x} 5 \phi_{4} + \Sigma_5
   \phi_5 = 0 \:.
  \end{gather}
  \label{eq:p5_equations}
\end{subequations}
This gives us a set of 6 coupled equations for the six Legendre
moments requested defined over the entire spatial domain for a single
energy group. In practice, only odd-numbered $P_N$ orders are
generally used \cite{lewis_computational_1993}. This is due to the
fact that using odd $N$ yields an even number of $N+1$ equations which
can be split evenly on the left and right boundaries of the problem to
facilitate the description of boundary conditions. We will choose this
convention when deriving the boundary conditions.

\subsection{Boundary Conditions for the $P_N$ Equations}
\label{subsbusec:bcs_pn}
Per the analysis in \cite{lewis_computational_1993}, two types of
boundary conditions will be discussed: reflecting and Marshak. Marshak
boundary conditions can be used to specify both vacuum conditions and
isotropic source conditions on the boundary.

>>>>

The neutron transport problem is complicated. Solutions cover a large
phase space and the problems of interest are often geometrically
complex, very large, or both, requiring tremendous computational
resources to generate an adequate solution. Modern deterministic
methods for large scale problems are commonly variants on the discrete
ordinates ($S_N$) method \citep{evans_denovo:_2010}. For full reactor
core neutronics simulations, the $S_N$ method requires potentially
trillions of unknown angular flux moments to be computed to achieve
good accuracy for the repsonses of interest. Other forms of the
transport problem, including the $P_N$ method, take on a simpler form
than the more common $S_N$ methods but lack in accuracy when compared
while still requiring considerable computational resources for
solutions in multiple dimensions.

@@

@@

%%---------------------------------------------------------------------------%%
\section{The Neutron Transport Equation}
\label{sec:transport_eq}
As a starting point we define the time-independent neutron transport
equation \citep{lewis_computational_1993}:
\begin{multline}
  \hat{\Omega} \cdot \vec{\nabla} \psi(\vec{r},\hat{\Omega},E) +
  \sigma(\vec{r},E) \psi(\vec{r},\hat{\Omega},E) = \\ \int \int
  \sigma_s(\vec{r},E' \rightarrow E,\hat{\Omega}' \rightarrow
  \hat{\Omega}) \psi(\vec{r},\hat{\Omega}',E') d\Omega' dE' +
  q(\vec{r},\hat{\Omega},E)\:,
  \label{eq:general_transport}
\end{multline}
with the variables defined as:
\begin{itemize}
\item $\vec{r}$ - neutron spatial position
\item $\hat{\Omega}$ - neutron streaming direction with radial
  component $\mu$ and azimuthal component $\omega$
\item $\hat{\Omega}' \cdot \hat{\Omega} = \mu_0$ is the angle of
  scattering
\item $E$ - neutron energy
\item $\psi(\vec{r},\hat{\Omega},E)$ - angular flux
\item $\sigma(\vec{r},E)$ - total interaction cross section
\item $\sigma_s(\vec{r},E' \rightarrow E,\hat{\Omega}')$ - probability
  of scattering from direction $\hat{\Omega}'$ into an angular domain
  $d\hat{\Omega}'$ about the direction $\hat{\Omega}$ and from energy
  $E'$ to an energy domain $dE'$ about energy $E$
\item $q(\vec{r},\hat{\Omega},E)$ - external source of neutrons.
\end{itemize}
For this work, it is sufficient to formulate
Eq~(\ref{eq:general_transport}) in 1-dimensonal Cartesian geometry:
\begin{multline}
  \mu \frac{\partial}{\partial x} \psi(x,\mu,E) + \sigma(x,E)
  \psi(x,\mu,E) = \\ \int \int \sigma_s(x,E') \rightarrow
  E,\hat{\Omega}' \rightarrow \hat{\Omega}) \psi(x,\hat{\Omega}',E')
  d\Omega' dE' + \frac{q(x,E)}{4 \pi}\:,
  \label{eq:cart_1d_transport}
\end{multline}
where the angular component of the solution is no longer dependent on
the azimuthal direction of travel and an isotropic source of neutrons
is assumed.

@@

\subsection{Legendre Polynomials}
\label{subsec:legendre_polys}
The Legendre polynomials are an orthogonal set of functions that
are solutions to Legendre's differential equation. They have the
following form \citep{lewis_computational_1993}:
\begin{equation}
  P_l(\mu) = \frac{1}{2^l l!}\frac{d^l}{d \mu^l}(\mu^2-1)^l\:.
  \label{eq:general_legendre_poly}
\end{equation}
These functions have several useful properties including
orthogonality:
\begin{equation}
  \int_{-1}^{1} P_l(\mu) P_{l'}(\mu) d\mu = \frac{1}{2l+1}\delta_{l l'}\:,
  \label{eq:legendre_orthog}
\end{equation}
a recurrence relation:
\begin{equation}
  \mu P_l(\mu) = \frac{1}{2l+1}[(l+1)P_{l+1}(\mu) + l P_{l-1}(\mu)]\:,
  \label{eq:legendre_recurrence}
\end{equation}
and an addition theorem:
\begin{equation}
  P_l(\hat{\Omega} \cdot \hat{\Omega}') = \frac{1}{2n+1}\sum_{m=-l}^l
  Y_{lm}(\hat{\Omega})Y^*_{lm}(\hat{\Omega}')\:,
  \label{eq:legendre_addition}
\end{equation}
where the functions $Y_{lm}(\hat{\Omega})$ are the spherical
harmonics. We can form the addition theorem in this way because the
spherical harmonics are in fact just harmonic multiples of the
Legendre polynomials:
\begin{equation}
  Y_{lm}(\hat{\Omega}) =
  \sqrt{\frac{(2l+1)(l-m)!}{(l+m)!}}P^m_l(\mu)e^{i \omega m}\:,
  \label{eq:spherical_harmonic}
\end{equation}
where $\omega$ is the azimuthal component of the streaming
direction. We can reduce Eq~(\ref{eq:legendre_addition}) for the
planar geometry we are studying by ignoring the azimuthal components
of the addition theorem. As shown in Eq~(\ref{eq:spherical_harmonic}),
the azimuthal dependence is given by the harmonic component, $e^{i
  \omega m}$, and therefore we choose to ignore all terms in
Eq.~(\ref{eq:legendre_addition}) where $m \neq 0$. This gives:
\begin{equation}
  P_l(\hat{\Omega} \cdot \hat{\Omega}') = \frac{1}{2n+1}
  Y_{l0}(\hat{\Omega})Y^*_{l0}(\hat{\Omega}')\:.
  \label{eq:legendre_addition_2}
\end{equation}
Per Eq~(\ref{eq:spherical_harmonic}) we have:
\begin{equation}
  Y_{l0}(\hat{\Omega}) = \sqrt{2l+1}P_l^0(\mu)\:,
  \label{eq:harmonic_0}
\end{equation}
where $P_l^0(\mu) = P_l(\mu)$ is the $0^{th}$ associated Legendre
function. Finally, we can reduce the addition theorem from
Eq~(\ref{eq:legendre_addition_2}) with Eq~(\ref{eq:harmonic_0}) to a
simple product for planar geometry:
\begin{equation}
  P_l(\hat{\Omega} \cdot \hat{\Omega}') = P_l(\mu)P_l(\mu')\:.
  \label{eq:legendre_addition_3}
\end{equation}

\subsection{Planar $P_N$ Equations}
\label{subsec:planar_pn}
With the Legendre polynomial properties defined above, we can proceed
by deriving the $P_N$ equations for planar geometry. For these
equations, we will start by assuming a monoenergtic field of neutrons
such that we are solving the following reduced form of the transport
equation: 
\begin{equation}
  \mu \frac{\partial}{\partial x} \psi(x,\mu) + \sigma(x) \psi(x,\mu)
  = \int \sigma_s(x,\hat{\Omega}' \rightarrow \hat{\Omega})
  \psi(\vec{r},\hat{\Omega}') d\Omega' + \frac{q(x)}{4 \pi}\:.
  \label{eq:mono_transport}
\end{equation}
The $P_N$ equations introduce the approximation that the angular
dependence of the scattering cross section, $\sigma_s$, and the angular
flux $\psi$, can be discretized by expanding them in Legendre
polynomials as follows:
\begin{equation}
  \psi(x,\mu) = \sum_{n=0}^\infty (2n+1)P_n(\mu)\phi_n(x)\:,
  \label{eq:flux_expansion}
\end{equation}
\begin{equation}
  \sigma_{sm}(x) = \sum_{m=0}^\infty (2m+1)P_m(\mu)\sigma_s(x)\:,
  \label{eq:scattering_expansion}
\end{equation}
where we have supressed the $2\pi$ generated by integrating away the
azimuthal angular component and $\phi_n(x)$ in
Eq~(\ref{eq:flux_expansion}) is referred to as the $n^{th}$ Legendre
moment of the neutron flux and is given by:
\begin{equation}
  \phi_n(x) = \int_{-1}^1 P_n(\mu)\psi(x,\mu)d\mu\:.
  \label{eq:legendre_moments}
\end{equation}
We first insert the expansions given by Eq~(\ref{eq:flux_expansion})
and (\ref{eq:scattering_expansion}) into the planar transport equation
given by Eq~(\ref{eq:mono_transport}):
\begin{multline}
  \frac{\partial}{\partial x}\Big[\sum_{n=0}^\infty (2n+1) \phi_n \mu
    P_n(\mu) \Big] + \sigma \sum_{n=0}^\infty (2n+1) \phi_n P_n(\mu) =
  \\ \int_{-1}^1 \sum_{m=0}^\infty (2m+1) \sigma_{sm} P_m(\mu_0)
  \sum_{n=0}^\infty (2n+1) \phi_n P_n(\mu') d \mu' + q\:,
  \label{eq:pn_deriv_1}
\end{multline}
where the dependence on the spatial variable, $x$, has been
supressed. To arrive at the $P_N$ equations we multiply
Eq~(\ref{eq:pn_deriv_1}) by $P_m(\mu)$ and integrate over the angular
domain $\int_{-1}^1 d \mu$. We will look at each term in
Eq~(\ref{eq:pn_deriv_1}) individually.

@@

Now that we have expanded all angular dependent terms in
Eq~(\ref{eq:pn_deriv_1}) and reduced them appropriately, we can
combine them to generate the $P_N$ equations:
\begin{equation}
    \sum_{n=0}^\infty \frac{\partial}{\partial x} \frac{1}{2n+1} \Big[
      (n+1) \phi_{n+1} + n \phi_{n-1} \Big] + \sum_{n=0}^\infty \sigma
    \phi_n = \sum_{n=0}^\infty \sigma_{sn} \phi_n + q\delta_{n0}\:.
  \label{eq:pn_deriv_18}
\end{equation}
More formally, the $P_N$ equations are written as:
\begin{equation}
   \frac{1}{2n+1} \frac{\partial}{\partial x}\Big[ (n+1) \phi_{n+1} + n
     \phi_{n-1} \Big] + \Sigma_n \phi_n = q\delta_{n0} \:,
  \label{eq:final_pn_equations}
\end{equation}
where $\Sigma_n = \sigma-\sigma_{sn}$ and the summations are truncated
at some level of approximation $N$ such that $n = 0,1,\dotsc,N$. This
yields a set of $N+1$ equations for $N+2$ flux moments. We therefore
require an additional equation to close the system. In accordance with
the series truncation as an approximation we choose the last moment in
the expansion to be zero:
\begin{equation}
  \phi_{N+1} = 0\:.
  \label{eq:pn_closure}
\end{equation}
As an example, we will construct the P5 equations from
Eq~(\ref{eq:final_pn_equations}) and the closure given by
Eq~(\ref{eq:pn_closure}):
\begin{subequations}
  \begin{gather}
   \frac{\partial}{\partial x}\phi_{1} + \Sigma_0 \phi_0 = q\:,\\ 
   \frac{1}{3} \frac{\partial}{\partial x}\Big[ 2
     \phi_{2} + \phi_{0} \Big] + \Sigma_1 \phi_1 = 0\:,\\
   \frac{1}{5} \frac{\partial}{\partial x}\Big[ 3 \phi_{3} + 2
     \phi_{1} \Big] + \Sigma_2 \phi_2 = 0 \:,\\
   \frac{1}{7} \frac{\partial}{\partial x}\Big[ 4 \phi_{4} + 3
     \phi_{2} \Big] + \Sigma_3 \phi_3 = 0 \:,\\
   \frac{1}{9} \frac{\partial}{\partial x}\Big[ 5 \phi_{5} + 4
     \phi_{3} \Big] + \Sigma_4 \phi_4 = 0 \:,\\
   \frac{1}{11} \frac{\partial}{\partial x} 5 \phi_{4} + \Sigma_5
   \phi_5 = 0 \:.
  \end{gather}
  \label{eq:p5_equations}
\end{subequations}
This gives us a set of 6 coupled equations for the six Legendre
moments requested defined over the entire spatial domain for a single
energy group. In practice, only odd-numbered $P_N$ orders are
generally used \citep{lewis_computational_1993}. This is due to the
fact that using odd $N$ yields an even number of $N+1$ equations which
can be split evenly on the left and right boundaries of the problem to
facilitate the description of boundary conditions. We will choose this
convention when deriving the boundary conditions.

\subsection{Boundary Conditions for the $P_N$ Equations}
\label{subsbusec:bcs_pn}
Per the analysis in \citep{lewis_computational_1993}, two types of
boundary conditions will be discussed: reflecting and Marshak. Marshak
boundary conditions can be used to specify both vacuum conditions and
isotropic source conditions on the boundary.
